---
title: "kidmid behavior"
output: pdf_document
---

```{r}
require(ggplot2)
setwd("~/Documents/ELS/KIDMID/Analysis/behavior")
d = read.csv("all_behavior_26-Aug-2014.csv", header=TRUE) #change to updated version

n = length(d$subID)
accuracy = data.frame(d$gain_acc,d$loss_acc,d$nongain_acc,d$nonloss_acc,d$total_acc)
rt = data.frame(d$rt_gain,d$rt_loss,d$rt_nongain,d$rt_nonloss,d$rt_mean)
counts = data.frame(d$gain_count, d$loss_count, d$nongain_count, d$nonloss_count)
#mean_rt = (d$rt_gain + d$rt_loss + d$rt_nongain + d$rt_nonloss)/4
#rt = data.frame(d$rt_gain,d$rt_loss,d$rt_nongain,d$rt_nonloss,mean_rt)
```

Summary statistics 
----------------------

--`r n` subjects 

### Accuracy
```{r accuracy}
plot1 = boxplot(accuracy, names = c("gain","loss","nongain","nonloss","total"),ylab=("percent successfully pressed before target"))
```

The total accuracy (`r round(mean(d$total_acc),3)*100`%) is lower than what is expected. Participants should be successfully pressing the button before the target-offset approximately 66% of the time.

**Gain**: mean = `r round(mean(d$gain_acc),3)*100`%; median = `r round(median(d$gain_acc),3)*100`%; min = `r round(min(d$gain_acc),3)*100`%; max = `r round(max(d$gain_acc),3)*100`%

**Loss**: mean = `r round(mean(d$loss_acc),3)*100`%; median = `r round(median(d$loss_acc),3)*100`%; min = `r round(min(d$loss_acc),3)*100`%; max = `r round(max(d$loss_acc),3)*100`%

**Nongain**: mean = `r round(mean(d$nongain_acc),3)*100`%; median = `r round(median(d$nongain_acc),3)*100`%; min = `r round(min(d$nongain_acc),3)*100`%; max = `r round(max(d$nongain_acc),3)*100`%

**Nonloss**: mean = `r round(mean(d$nonloss_acc),3)*100`%; median = `r round(median(d$nonloss_acc),3)*100`%; min = `r round(min(d$nonloss_acc),3)*100`%; max = `r round(max(d$nonloss_acc),3)*100`%

**All trials**: mean = `r round(mean(d$total_acc),3)*100`%; median = `r round(median(d$total_acc),3)*100`%; min = `r round(min(d$total_acc),3)*100`%; max = `r round(max(d$total_acc),3)*100`%

```{r total_acc}
hist(d$total_acc)
summary(d$total_acc)
total.out = boxplot.stats(d$total_acc, do.out=TRUE)
total.out$out
```

```{r gain_acc}
hist(d$gain_acc)
summary(d$gain_acc)
gain_acc.out = boxplot.stats(d$gain_acc, do.out=TRUE)
gain_acc.out$out
```

```{r loss_acc}
hist(d$loss_acc)
summary(d$loss_acc)
loss_acc.out = boxplot.stats(d$loss_acc, do.out=TRUE)
loss_acc.out$out
```

```{r nongain_acc}
hist(d$nongain_acc)
summary(d$nongain_acc)
nongain_acc.out = boxplot.stats(d$nongain_acc, do.out=TRUE)
nongain_acc.out$out
```

```{r nonloss_acc}
hist(d$nonloss_acc)
summary(d$nonloss_acc)
nonloss_acc.out = boxplot.stats(d$nonloss_acc, do.out=TRUE)
nonloss_acc.out$out
```

### Missed Trials

```{r missed}
plot2 = boxplot(d$missed_percent,ylab=("percent of trials when no button was pressed"))
```

**Outliers**
```{r outliers}
missed.out = boxplot.stats(d$missed_percent,do.out = TRUE)
missed.out$out
hist(d$missed_percent)
```

### Response Time
```{r rt}
plot3 = boxplot(rt, names = c("gain","loss","nongain","nonloss","mean"),ylab=("response time (ms)"))
```

**Gain**: mean = `r round(mean(rt$d.rt_gain),2)` ms; median = `r round(median(rt$d.rt_gain),2)` ms; min = `r round(min(rt$d.rt_gain),2)` ms; max = `r round(max(rt$d.rt_gain),2)` ms

**Loss**: mean = `r round(mean(rt$d.rt_loss),2)` ms; median = `r round(median(rt$d.rt_loss),2)` ms; min = `r round(min(rt$d.rt_loss),2)` ms; max = `r round(max(rt$d.rt_loss),2)` ms

**Nongain**: mean = `r round(mean(rt$d.rt_nongain),2)` ms; median = `r round(median(rt$d.rt_nongain),2)` ms; min = `r round(min(rt$d.rt_nongain),2)` ms; max = `r round(max(rt$d.rt_nongain),2)` ms

**Nonloss**: mean = `r round(mean(rt$d.rt_nonloss),2)` ms; median = `r round(median(rt$d.rt_nonloss),2)` ms; min = `r round(min(rt$d.rt_nonloss),2)` ms; max = `r round(max(rt$d.rt_nonloss),2)` ms

**All trials**: mean = `r round(mean(rt$d.rt_mean),2)` ms; median = `r round(median(rt$d.rt_mean),2)` ms; min = `r round(min(rt$d.rt_mean),2)` ms; max = `r round(max(rt$d.rt_mean),2)` ms

```{r rt_gain}
hist(d$rt_gain)
summary(d$rt_gain)
gain_rt.out = boxplot.stats(d$rt_gain, do.out=TRUE)
gain_rt.out$out
```

```{r rt_loss}
hist(d$rt_loss)
summary(d$rt_loss)
rt_loss.out = boxplot.stats(d$rt_loss, do.out=TRUE)
rt_loss.out$out
```

```{r rt_nongain}
hist(d$rt_nongain)
summary(d$rt_nongain)
rt_nongain.out = boxplot.stats(d$rt_nongain, do.out=TRUE)
rt_nongain.out$out
```

```{r rt_nonloss}
hist(d$rt_nonloss)
summary(d$rt_nonloss)
rt_nonloss.out = boxplot.stats(d$rt_nonloss, do.out=TRUE)
rt_nonloss.out$out
```

```{rt_mean}
hist(d$rt_mean)
summary(d$rt_mean)
rt_mean.out = boxplot.stats(d$rt_mean, do.out=TRUE)
rt_mean.out$out
```

### Number of trials going into the single-subject model

```{r outcome counts}
plot4 = boxplot(counts, names = c("gain","loss","nongain","nonloss"), ylab="number of trials in outcome analysis per subject")
counts.m = as.matrix(counts)


barplot(counts.m,names.arg = c("gain","loss","nongain","nonloss"), ylab = "total number of trials in outcome analysis", col = " light blue", main = "Total number of trials in outcome analysis for all subjects")
# text(.5,865, sum(d$gain_count))
# text(1.5, sum(d$gain_count))

```

```{r gain outcome counts}
hist(d$gain_count)
summary(d$gain_count)
gain_count.out = boxplot.stats(d$gain_count, do.out=TRUE)
gain_count.out$out
```

```{r loss outcome counts}
hist(d$loss_count)
summary(d$loss_count)
loss_count.out = boxplot.stats(d$loss_count, do.out=TRUE)
loss_count.out$out
```

```{r nongain outcome counts}
hist(d$nongain_count)
summary(d$nongain_count)
nongain_count.out = boxplot.stats(d$nongain_count, do.out=TRUE)
nongain_count.out$out
```

```{r nonloss outcome counts}
hist(d$nonloss_count)
summary(d$nonloss_count)
nonloss_count.out = boxplot.stats(d$nonloss_count, do.out=TRUE)
nonloss_count.out$out
```

