---
title: "Gender, ELS, kidmid"
output: html_document
---

```{r load in data}
require(ggplot2)
setwd("~/Documents/ELS/KIDMID/Analysis/ROI/70N_Model5.1")
a = read.csv("Model5.1_RNacc_HO_anticipation24-Mar-2015.csv")
o = read.csv("Model5.1_RNacc_HO_outcome24-Mar-2015.csv")
setwd("~/Documents/ELS/KIDMID/Analysis/behavior")
b = read.csv("all_behavior_10-Feb-2015.csv")
#removing behavioral outliers and #removing noisey subjects
b = b[-c(14,15,24,26,33,38),] 
```

```{r}
#is version correlated with ELS?
#as.factor(b$gender)
factor(b$gender)
#as.factor(b$v2)
factor(b$v2)
cor.test(b$v2,b$ELS.subj) #p = .01
cor.test(b$gender,b$ELS.subj) #p = .18

plot(b$ELS.subj,b$v2)
mean(b$ELS.subj[b$v2==1]) #9.85
mean(b$ELS.subj[b$v2==2]) #5.40

plot(b$ELS.subj,b$gender)
mean(b$ELS.subj[b$gender==1]) #6.93
mean(b$ELS.subj[b$gender==2]) #4.96

summary(lm(b$ELS.subj ~ b$gender + b$v2)) #gender effect ns, v2 effect p = .03
```

The version of the task is related to ELS - kids who had the first version of the task have higher mean ELS.subj scores than kids who had the second version of the task. Gender is not related to ELS.

```{r merge data}
d = cbind(b,a,o) #merge data frames
d$gender = as.factor(d$gender)
d$v2 = as.factor(d$v2)
levels(d$gender) = c("female","male")

hist(d$ELS.subj)
d$ELS.subjcat2 = cut(d$ELS.subj, c(0,5,10,30), right=FALSE, labels=c("low","int","high")) 
d$ELS.subjcat3 = cut(d$ELS.subj, c(0,5,30), right=FALSE, labels=c("low","high"))
table(d$ELS.subjcat2)
table(d$ELS.subjcat3)
```

RNAcc
----------
```{r}
#is ELS and/or gender related to RNAcc ant activation (controlling for version)

#ant gain
summary(lm(d$rNAcc.antgain ~ d$ELS.subj)) #ns
summary(lm(d$rNAcc.antgain ~ d$ELS.subjcat2)) #ns
summary(lm(d$rNAcc.antgain ~ d$ELS.subj + d$v2)) #ns
summary(lm(d$rNAcc.antgain ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain ~ (d$ELS.subj * d$gender) + d$v2)) #ns
summary(lm(d$rNAcc.antgain ~ d$ELS.subjcat2 + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain ~ d$ELS.subjcat2 + d$v2 + d$gender + d$rt_gain)) #ns
summary(lm(d$rNAcc.antgain ~ d$gender)) #ns
#ant loss
summary(lm(d$rNAcc.antloss ~ d$ELS.subj)) #ns
summary(lm(d$rNAcc.antloss ~ d$gender + d$v2))
summary(lm(d$rNAcc.antloss ~ d$ELS.subjcat2)) #ns
summary(lm(d$rNAcc.antloss ~ d$ELS.subj + d$v2)) #ns
summary(lm(d$rNAcc.antloss ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antloss ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antloss ~ (d$ELS.subj * d$gender) + d$v2)) #ns
summary(lm(d$rNAcc.antloss ~ d$ELS.subjcat2 + d$v2 + d$gender)) #ns, p=.08 for high ELS v low ELS but no effect for ELS.subjcat3
summary(lm(d$rNAcc.antloss ~ d$ELS.subjcat2 + d$v2 + d$gender + d$rt_loss)) #ns

#ant gain v nongain
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subj)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subjcat2)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subjcat3 + d$v2)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$v2 + d$gender))
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ (d$ELS.subj * d$gender) + d$v2)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antnongain ~ d$ELS.subj + d$v2 + d$gender + d$rt_gain)) #ns

#ant loss v nonloss
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subj)) #ns
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subjcat2)) # ELS high vs low, p = .04

plot(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subjcat2)

summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subjcat2 + d$v2)) # ELS high vs low, p = .01, version p =.01
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subjcat2 + d$v2 + d$rt_loss)) #ELS high vs low, version still sig
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subjcat2 + d$v2 + d$rt_loss-d$rt_nonloss)) #ELS high vs low, version still sig

lo.mean = mean((d$rNAcc.antloss-d$rNAcc.antnonloss)[d$ELS.subjcat2=="low"])
int.mean = mean((d$rNAcc.antloss-d$rNAcc.antnonloss)[d$ELS.subjcat2=="int"])
hi.mean = mean((d$rNAcc.antloss-d$rNAcc.antnonloss)[d$ELS.subjcat2=="high"])
barplot(height=c(lo.mean,int.mean,hi.mean))
t.test((d$rNAcc.antloss-d$rNAcc.antnonloss)[d$ELS.subjcat2=="low"],(d$rNAcc.antloss-d$rNAcc.antnonloss)[d$ELS.subjcat2=="high"])
#p = .06
#Difference between RNacc antloss and nonloss activation is greater for high ELS vs low ELS.

summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subjcat2 + d$v2 + d$gender)) # ELS high vs low p = .01, version p =.03

summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subj + d$v2 + d$gender)) #p = .05 for ELS

summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ (d$ELS.subjcat3 * d$gender) + d$v2)) #ns
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$gender)) #ns
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subj + d$v2 + d$gender)) #ELS effect p = .05, no effect for gender
summary(lm(d$rNAcc.antloss-d$rNAcc.antnonloss ~ d$ELS.subj + d$v2 + d$gender + d$rt_loss)) #ns

#ant gain v loss
summary(lm(d$rNAcc.antgain-d$rNAcc.antloss ~ d$gender + d$v2)) #ns
summary(lm(d$rNAcc.antgain-d$rNAcc.antloss ~ (d$gender * d$ELS.subjcat3) + d$v2)) #ns
```
When controlling for version, the difference between activation in right NAcc for anticipation of loss vs nonloss is assoc. with greater ELS. There is no effect of gender on R NAcc and there is no interaction of gender and ELS.



```{r}
#is ELS and/or gender related to RNAcc outcome activation (controlling for version)

#out gain
summary(lm(d$rNAcc.gain ~ d$ELS.subj)) #p =.05
summary(lm(d$rNAcc.gain ~ d$ELS.subj + d$v2)) #p = .03 
cor.test(d$rNAcc.gain,d$ELS.subj) #r = .23, p = .05
p1 = plot(d$rNAcc.gain ~ d$ELS.subj)
abline(lm(d$rNAcc.gain ~ d$ELS.subj + d$v2))

summary(lm(d$rNAcc.gain ~ d$ELS.subjcat2)) #high v low ELS p = .05
summary(lm(d$rNAcc.gain ~ d$ELS.subjcat3)) #high v low ELS p = .07


summary(lm(d$rNAcc.gain ~ d$ELS.subj + d$v2 + d$gender)) #ELS p = .04, gender p = .09
summary(lm(d$rNAcc.gain ~ d$ELS.subjcat2 + d$v2 + d$gender)) #ns high vs low ELS p = .05, gender p = .09
summary(lm(d$rNAcc.gain ~ (d$ELS.subjcat3 * d$gender) + d$v2)) #ns no interaction
summary(lm(d$rNAcc.gain ~ d$ELS.subj + d$v2 + d$gender + d$rt_gain)) #ELS p = .04
summary(lm(d$rNAcc.gain ~ d$gender)) #ns


#out loss
summary(lm(d$rNAcc.loss ~ d$ELS.subj)) #ns
summary(lm(d$rNAcc.loss ~ d$gender)) #p = .08
summary(lm(d$rNAcc.loss ~ d$gender + d$v2)) #gender p = .06
summary(lm(d$rNAcc.loss ~ d$ELS.subjcat3 + d$v2)) #ns
summary(lm(d$rNAcc.loss ~ d$ELS.subj + d$v2)) #ns
summary(lm(d$rNAcc.loss ~ d$ELS.subj + d$v2 + d$gender)) #gender p = .06
summary(lm(d$rNAcc.loss ~ d$ELS.subjcat2 + d$v2 + d$gender)) #gender p = .05
summary(lm(d$rNAcc.loss ~ d$ELS.subjcat3 + d$v2 + d$gender)) #gender p = .06
summary(lm(d$rNAcc.loss ~ (d$ELS.subj * d$gender) + d$v2)) #gender p = .07
summary(lm(d$rNAcc.loss ~ (d$ELS.subjcat3 * d$gender) + d$v2)) #gender p = .08
summary(lm(d$rNAcc.loss ~ d$ELS.subjcat2 + d$v2 + d$gender + d$rt_loss)) #gender p=.07
summary(lm(d$rNAcc.loss ~ d$ELS.subjcat3 + d$v2 + d$gender + d$rt_loss)) #gender p=.07
summary(lm(d$rNAcc.loss ~ d$ELS.subj + d$v2 + d$gender + d$rt_loss)) #gender p=.08

#out gain v nongain
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj)) #p = .08
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj + d$v2)) #p = .04
p2 = plot(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj)
abline(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj))

summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subjcat3)) #ns
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subjcat2 + d$v2)) #ns
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj + d$v2 + d$gender)) #ns
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$v2 + d$gender)) #ns

summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj * d$gender)) 
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ (d$ELS.subj * d$gender) + d$v2)) #main effect ELS p = .05, interaction gender and ELS p = .02, model sig p=.01
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ (d$ELS.subjcat3 * d$gender) + d$v2)) #ns
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ (d$ELS.subj * d$gender) + d$v2 + (d$rt_gain-d$rt_nongain))) #same as above, main model sig p=.03
summary(lm(d$rNAcc.gain-d$rNAcc.nongain ~ d$ELS.subj + d$v2 + d$gender + d$rt_gain)) #ns

library(psych)
describeBy(d$ELS.subj, d$gender, mat = TRUE)

colors = c("indianred1","orange")

d$rNAcc.gainvnongain = d$rNAcc.gain-d$rNAcc.nongain
ggplot(data = d, aes(x=ELS.subj, y = rNAcc.gainvnongain, color = gender)) + scale_color_manual(values=colors) +
  theme_bw() +
  geom_point(size=4) + stat_smooth(method="lm") +
  #theme(plot.title = element_text(size = 15, hjust=0.5)) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #theme(legend.key = element_rect(fill = "white")) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_text(size = 20)) + 
  theme(axis.text = element_text(size = 20, color = "black"))
  

#theme(panel.grid.major = element_blank())

#theme(panel.grid.major = element_blank(),
   #labs(x="Early Life Stress", y="% BOLD Signal Change during Outcome of Gain - Nongain") +
  #ggtitle("Right Nucleus Accumbens Activity \n During Outcome of Gain - Nongain \n is Moderated by Gender")


restricted.ELS = subset(d, d$ELS.subj <= 20)
summary(lm(restricted.ELS$rNAcc.gain-restricted.ELS$rNAcc.nongain ~ (restricted.ELS$ELS.subj * restricted.ELS$gender) + restricted.ELS$v2))
#interaction.plot(x.factor = d$ELS.subj, trace.factor = d$gender, response = d$rNAcc.gainvnongain, type = c("l"))

#out gain v loss
d$rNAcc.gainvloss = d$rNAcc.gain-d$rNAcc.loss
summary(lm(d$rNAcc.gainvloss ~ d$ELS.subj * d$gender)) 
summary(lm(d$rNAcc.gainvloss ~ (d$ELS.subj * d$gender) + d$v2)) 
summary(lm(d$rNAcc.gainvloss ~ d$ELS.subj + d$v2))
summary(lm(d$rNAcc.gainvloss ~ d$ELS.subj + d$gender + d$v2))
```

When controlling for version, the ELS is associated with greater activation during outcome of gains > baseline in rNAcc. 

R NAcc activation for outcome of loss > baseline is weakly related to gender (p=.05, when controlling for version and 3-level ELS).

The differene between activation for outcome of gain v nongain is related to ELS (p=.04, controlling for version).


```{r}
setwd("~/Documents/ELS/KIDMID/Analysis/ROI/70N_Model5.1")
out = read.csv("featquery_outcome26-Mar-2015.csv")
out = cbind(out,b)
out$gender = as.factor(out$gender)
out$v2 = as.factor(out$v2)
levels(out$gender) = c("F","M")

out$ELS.subjcat2 = cut(out$ELS.subj, c(0,5,10,30), right=FALSE, labels=c("low","int","high")) 
out$ELS.subjcat3 = cut(out$ELS.subj, c(0,5,30), right=FALSE, labels=c("low","high"))

ant = read.csv("featquery_anticipation26-Mar-2015.csv")
ant = cbind(ant,b)
ant$gender = as.factor(ant$gender)
ant$v2 = as.factor(ant$v2)
levels(ant$gender) = c("F","M")
ant$ELS.subjcat2 = cut(ant$ELS.subj, c(0,5,10,30), right=FALSE, labels=c("low","int","high")) 
ant$ELS.subjcat3 = cut(ant$ELS.subj, c(0,5,30), right=FALSE, labels=c("low","high"))

```

OUTCOME
============

Left Caudate
----------------
```{r}
#gain v nongain - marginal gender interaction with continuous, significant with hi int low
summary(lm(out$Lcaud_gain-out$Lcaud_nongain ~ out$ELS.subj + out$v2)) 
summary(lm(out$Lcaud_gain-out$Lcaud_nongain ~ out$ELS.subj + out$gender + out$v2)) #ns
summary(lm(out$Lcaud_gain-out$Lcaud_nongain ~ (out$ELS.subj * out$gender) + out$v2)) #interaction term p = .06
summary(lm(out$Lcaud_gain-out$Lcaud_nongain ~ (out$ELS.subjcat2 * out$gender) + out$v2)) #high v low interaction term p = .04
summary(lm(out$Lcaud_gain-out$Lcaud_nongain ~ (out$ELS.subjcat3 * out$gender) + out$v2)) #ns

out$Lcaud_gainvnongain = out$Lcaud_gain-out$Lcaud_nongain
ggplot(data = out, aes(x=ELS.subj, y = Lcaud_gainvnongain, color=gender)) +
  geom_point(size=4) + stat_smooth(method="lm") + theme(panel.grid.major = element_blank(), plot.title = element_text(size = 15, hjust=0.5)) + 
  labs(x = "Early Life Stress", y = "Percent BOLD signal change \n Outcome of Gain - Nongain") +
  ggtitle("Left Caudate Activity \n During Outcome of Gain - Nongain \n is Moderated by Gender")

#gain
summary(lm(out$Lcaud_gain ~ out$ELS.subj + out$v2)) #ns
summary(lm(out$Lcaud_gain ~ (out$ELS.subjcat3 * out$gender) + out$v2)) #ns

#loss v nonloss - no gender interaction
summary(lm(out$Lcaud_loss-out$Lcaud_nonloss ~ out$ELS.subj + out$v2)) # p = .001
summary(lm(out$Lcaud_loss-out$Lcaud_nonloss ~ out$ELS.subj + out$v2 + out$rt_loss-out$rt_nonloss)) #p = .001
summary(lm(out$Lcaud_loss-out$Lcaud_nonloss ~ out$ELS.subj + out$gender + out$v2)) #p = .001
summary(lm(out$Lcaud_loss-out$Lcaud_nonloss ~ (out$ELS.subj * out$gender) + out$v2)) #interaction term not significant
summary(lm(out$Lcaud_loss-out$Lcaud_nonloss ~ (out$ELS.subjcat2 * out$gender) + out$v2)) #interaction term not significant
summary(lm(out$Lcaud_loss-out$Lcaud_nonloss ~ (out$ELS.subjcat3 * out$gender) + out$v2)) #interaction term not significant

###ELS EFFECTS
#rearrange data to make bargraphs for ELS and condition effects 
ELScond = c(rep(x=out$ELS.subjcat3, times = 4)) #rep d$ELS.subjcat2 vector 4 times
Lcaud.pe = c(out$Lcaud_gain,out$Lcaud_nongain,out$Lcaud_loss,out$Lcaud_nonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
Lcaudbar.els = data.frame(condition.2,Lcaud.pe,ELScond) #concatenate vectors
Lcaud.means = aggregate(Lcaudbar.els$Lcaud.pe, list(ELS = Lcaudbar.els$ELScond, cond = Lcaudbar.els$condition.2), mean) #sort pe means by condition and ELS cat
Lcaud.sd = aggregate(Lcaudbar.els$Lcaud.pe, list(ELS = Lcaudbar.els$ELScond, cond = Lcaudbar.els$condition.2), sd)
Lcaud.n = aggregate(Lcaudbar.els$Lcaud.pe, list(ELS = Lcaudbar.els$ELScond, cond = Lcaudbar.els$condition.2), length)

Lcaud.summary.els = data.frame(
  Lcaud.means,  #x = mean
  sd = Lcaud.sd[3], #x.1 = sd
  n = Lcaud.n[3]) #x.2 = n

#calculate standard error of the mean 
Lcaud.summary.els$sem = Lcaud.summary.els$x.1/sqrt(Lcaud.summary.els$x.2) 
factor(Lcaud.summary.els$ELS)
Lcaud.summary.els$ELS = c(rep(c("low","high"), times = 4))

colors = rep(c("violetred4","red3"),4)

limits = aes(ymin=x-sem, ymax=x+sem)
g2.ELS = ggplot(Lcaud.summary.els, aes(x = cond, y = x, fill = ELS)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  #ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #theme(legend.key = element_rect(fill = "white")) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_text(size = 20)) + 
  theme(axis.text = element_text(size = 20)) +
  scale_fill_manual(values=colors)
print(g2.ELS)




```

Left Putamen
--------------------
```{r}
#gain v nongain
summary(lm(out$Lput_gain-out$Lput_nongain ~ out$ELS.subj + out$v2)) #ns
summary(lm(out$Lput_gain-out$Lput_nongain ~ out$ELS.subj + out$gender + out$v2)) #ns
summary(lm(out$Lput_gain-out$Lput_nongain ~ (out$ELS.subj * out$gender) + out$v2)) #ns
summary(lm(out$Lput_gain-out$Lput_nongain ~ (out$ELS.subjcat2 * out$gender) + out$v2)) #ns
summary(lm(out$Lput_gain-out$Lput_nongain ~ (out$ELS.subjcat3 * out$gender) + out$v2)) #ns

#loss v nonloss
summary(lm(out$Lput_loss-out$Lput_nonloss ~ out$ELS.subj + out$v2)) #p=.01
summary(lm(out$Lput_loss-out$Lput_nonloss ~ out$ELS.subj + out$gender + out$v2)) #p=.02
summary(lm(out$Lput_loss-out$Lput_nonloss ~ (out$ELS.subj * out$gender) + out$v2))
summary(lm(out$Lput_loss-out$Lput_nonloss ~ (out$ELS.subjcat3 * out$gender) + out$v2))


ELScond = c(rep(x=out$ELS.subjcat3, times = 4)) #rep d$ELS.subjcat2 vector 4 times
Lput.pe = c(out$Lput_gain,out$Lput_nongain,out$Lput_loss,out$Lput_nonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
Lputbar.els = data.frame(condition.2,Lput.pe,ELScond) #concatenate vectors
Lput.means = aggregate(Lputbar.els$Lput.pe, list(ELS = Lputbar.els$ELScond, cond = Lputbar.els$condition.2), mean) #sort pe means by condition and ELS cat
Lput.sd = aggregate(Lputbar.els$Lput.pe, list(ELS = Lputbar.els$ELScond, cond = Lputbar.els$condition.2), sd)
Lput.n = aggregate(Lputbar.els$Lput.pe, list(ELS = Lputbar.els$ELScond, cond = Lputbar.els$condition.2), length)

Lput.summary.els = data.frame(
  Lput.means,  #x = mean
  sd = Lput.sd[3], #x.1 = sd
  n = Lput.n[3]) #x.2 = n

#calculate standard error of the mean 
Lput.summary.els$sem = Lput.summary.els$x.1/sqrt(Lput.summary.els$x.2) 
factor(Lput.summary.els$ELS)
Lput.summary.els$ELS = c(rep(c("low","high"), times = 4))

colors = rep(c("violetred4","red3"),4)

limits = aes(ymin=x-sem, ymax=x+sem)
g3.ELS = ggplot(Lput.summary.els, aes(x = cond, y = x, fill = ELS)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  #ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #theme(legend.key = element_rect(fill = "white")) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_text(size = 20)) + 
  theme(axis.text = element_text(size = 20)) +
  scale_fill_manual(values=colors)
print(g3.ELS)



```

ANTICIPATION
=======================

Right Insula
--------------
```{r}
#ant gain v nongain - no interaction
summary(lm(ant$Rins_gain-ant$Rins_nongain ~ ant$ELS.subj + ant$v2)) #ns
summary(lm(ant$Rins_gain-ant$Rins_nongain ~ ant$ELS.subj + ant$gender + ant$v2)) #ns
summary(lm(ant$Rins_gain-ant$Rins_nongain ~ (ant$ELS.subj * ant$gender) + ant$v2)) #ns
summary(lm(ant$Rins_gain-ant$Rins_nongain ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2))
summary(lm(ant$Rins_gain-ant$Rins_nongain ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

#ant loss v nonloss
summary(lm(ant$Rins_loss-ant$Rins_nonloss ~ ant$ELS.subj + ant$v2)) # p =.0008
summary(lm(ant$Rins_loss-ant$Rins_nonloss ~ ant$ELS.subj + ant$gender + ant$v2))
summary(lm(ant$Rins_loss-ant$Rins_nonloss ~ (ant$ELS.subj * ant$gender) + ant$v2))
summary(lm(ant$Rins_loss-ant$Rins_nonloss ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) #interaction p=.09
summary(lm(ant$Rins_loss-ant$Rins_nonloss ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

ELScond = c(rep(x=ant$ELS.subjcat3, times = 4)) #rep d$ELS.subjcat2 vector 4 times
Rins.pe = c(ant$Rins_gain,ant$Rins_nongain,ant$Rins_loss,ant$Rins_nonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
Rinsbar.els = data.frame(condition.2,Rins.pe,ELScond) #concatenate vectors
Rins.means = aggregate(Rinsbar.els$Rins.pe, list(ELS = Rinsbar.els$ELScond, cond = Rinsbar.els$condition.2), mean) #sort pe means by condition and ELS cat
Rins.sd = aggregate(Rinsbar.els$Rins.pe, list(ELS = Rinsbar.els$ELScond, cond = Rinsbar.els$condition.2), sd)
Rins.n = aggregate(Rinsbar.els$Rins.pe, list(ELS = Rinsbar.els$ELScond, cond = Rinsbar.els$condition.2), length)

Rins.summary.els = data.frame(
  Rins.means,  #x = mean
  sd = Rins.sd[3], #x.1 = sd
  n = Rins.n[3]) #x.2 = n

#calculate standard error of the mean 
Rins.summary.els$sem = Rins.summary.els$x.1/sqrt(Rins.summary.els$x.2) 
factor(Rins.summary.els$ELS)
Rins.summary.els$ELS = c(rep(c("low","high"), times = 4))

colors = rep(c("violetred4","red3"),4)

limits = aes(ymin=x-sem, ymax=x+sem)
g4.ELS = ggplot(Rins.summary.els, aes(x = cond, y = x, fill = ELS)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  #ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #theme(legend.key = element_rect(fill = "white")) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_text(size = 20)) + 
  theme(axis.text = element_text(size = 20)) +
  scale_fill_manual(values=colors)
print(g4.ELS)


```

Right Putamen
------------------

```{r}
#gain v nongain
summary(lm(ant$Rput_gain-ant$Rput_nongain ~ ant$ELS.subj + ant$v2)) #ns
summary(lm(ant$Rput_gain-ant$Rput_nongain ~ ant$ELS.subj + ant$gender + ant$v2)) #ns
summary(lm(ant$Rput_gain-ant$Rput_nongain ~ (ant$ELS.subj * ant$gender) + ant$v2)) #ns
summary(lm(ant$Rput_gain-ant$Rput_nongain ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) #ns
summary(lm(ant$Rput_gain-ant$Rput_nongain ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2)) #ns

summary(lm(ant$Rput_loss-ant$Rput_nonloss ~ ant$ELS.subj + ant$v2)) #p=.0001
summary(lm(ant$Rput_loss-ant$Rput_nonloss ~ ant$ELS.subj + ant$gender + ant$v2))
summary(lm(ant$Rput_loss-ant$Rput_nonloss ~ (ant$ELS.subj * ant$gender) + ant$v2)) #interaction is not significant
summary(lm(ant$Rput_loss-ant$Rput_nonloss ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) 
summary(lm(ant$Rput_loss-ant$Rput_nonloss ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))
```

Right Caudate
--------------------
```{r}
summary(lm(ant$Rcaud_gain-ant$Rcaud_nongain ~ ant$ELS.subj + ant$v2)) #ns
summary(lm(ant$Rcaud_gain-ant$Rcaud_nongain ~ ant$ELS.subj + ant$gender + ant$v2)) #ns
summary(lm(ant$Rcaud_gain-ant$Rcaud_nongain ~ (ant$ELS.subj * ant$gender) + ant$v2)) #ns
summary(lm(ant$Rcaud_gain-ant$Rcaud_nongain ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2))
summary(lm(ant$Rcaud_gain-ant$Rcaud_nongain ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

#ant loss v nonloss
summary(lm(ant$Rcaud_loss-ant$Rcaud_nonloss ~ ant$ELS.subj + ant$v2)) 
summary(lm(ant$Rcaud_loss-ant$Rcaud_nonloss ~ ant$ELS.subj + ant$gender + ant$v2))
summary(lm(ant$Rcaud_loss-ant$Rcaud_nonloss ~ (ant$ELS.subj * ant$gender) + ant$v2))
summary(lm(ant$Rcaud_loss-ant$Rcaud_nonloss ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) 
summary(lm(ant$Rcaud_loss-ant$Rcaud_nonloss ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))
```

Left Caudate
--------------------
```{r}
summary(lm(ant$Lcaud_gain-ant$Lcaud_nongain ~ ant$ELS.subj + ant$v2)) #ns
summary(lm(ant$Lcaud_gain-ant$Lcaud_nongain ~ ant$ELS.subj + ant$gender + ant$v2)) #ns
summary(lm(ant$Lcaud_gain-ant$Lcaud_nongain ~ (ant$ELS.subj * ant$gender) + ant$v2)) #ns
summary(lm(ant$Lcaud_gain-ant$Lcaud_nongain ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2))
summary(lm(ant$Lcaud_gain-ant$Lcaud_nongain ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

#ant loss v nonloss
summary(lm(ant$Lcaud_loss-ant$Lcaud_nonloss ~ ant$ELS.subj + ant$v2)) 
summary(lm(ant$Lcaud_loss-ant$Lcaud_nonloss ~ ant$ELS.subj + ant$gender + ant$v2))
summary(lm(ant$Lcaud_loss-ant$Lcaud_nonloss ~ (ant$ELS.subj * ant$gender) + ant$v2))
summary(lm(ant$Lcaud_loss-ant$Lcaud_nonloss ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) 
summary(lm(ant$Lcaud_loss-ant$Lcaud_nonloss ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

#plot main effect
Lcaud.pe = c(ant$Lcaud_gain,ant$Lcaud_nongain,ant$Lcaud_loss,ant$Lcaud_nonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
Lcaudbar = data.frame(condition.2,Lcaud.pe)

Lcaud.summary = data.frame(
  condition = levels(Lcaudbar$condition.2),
  mean = tapply(Lcaudbar$Lcaud.pe, Lcaudbar$condition, mean),
  n = tapply(Lcaudbar$Lcaud.pe, Lcaudbar$condition, length),
  sd = tapply(Lcaudbar$Lcaud.pe, Lcaudbar$condition, sd)
  )

#calculate standard error of the mean 
Lcaud.summary$sem = Lcaud.summary$sd/sqrt(Lcaud.summary$n) 

#calculate margin of error for CI
alpha = .05 #95% confidence interval
Lcaud.summary$me = qt(1-alpha/2, df = Lcaud.summary$n)*Lcaud.summary$sem

#error bars represent standard error of the mean
g2.SE = ggplot(Lcaud.summary, aes(x = condition, y = mean)) + 
  geom_bar(position = position_dodge(), stat="identity", fill="red", width=.5) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.3) +
  labs(x = "Anticipation", y = "Percent BOLD signal change in L Caud") +
  #scale_y_continuous(limits=c(-.3, .4)) +
  ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank())
print(g2.SE)

#plotting ELS
ELScond = c(rep(x=ant$ELS.subjcat3, times = 4)) #rep d$ELS.subjcat2 vector 4 times
Lcaudbar.els = data.frame(condition.2,Lcaud.pe,ELScond) #concatenate vectors
Lcaud.means = aggregate(Lcaudbar.els$Lcaud.pe, list(ELS = Lcaudbar.els$ELScond, cond = Lcaudbar.els$condition.2), mean) #sort pe means by condition and ELS cat
Lcaud.sd = aggregate(Lcaudbar.els$Lcaud.pe, list(ELS = Lcaudbar.els$ELScond, cond = Lcaudbar.els$condition.2), sd)
Lcaud.n = aggregate(Lcaudbar.els$Lcaud.pe, list(ELS = Lcaudbar.els$ELScond, cond = Lcaudbar.els$condition.2), length)

Lcaud.summary.els = data.frame(
  Lcaud.means,  #x = mean
  sd = Lcaud.sd[3], #x.1 = sd
  n = Lcaud.n[3]) #x.2 = n

#calculate standard error of the mean 
Lcaud.summary.els$sem = Lcaud.summary.els$x.1/sqrt(Lcaud.summary.els$x.2) 
factor(Lcaud.summary.els$ELS)
#Lcaud.summary.els$ELS = c(rep(c("low","int","high"), times = 4))
Lcaud.summary.els$ELS = c(rep(c("low","high"), times = 4))

limits = aes(ymin=x-sem, ymax=x+sem)
g2.ELS = ggplot(Lcaud.summary.els, aes(x = cond, y = x, fill = ELS)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank())
print(g2.ELS)




```

Left Putamen
--------------------
```{r}
summary(lm(ant$Lput_gain-ant$Lput_nongain ~ ant$ELS.subj + ant$v2)) #ns
summary(lm(ant$Lput_gain-ant$Lput_nongain ~ ant$ELS.subj + ant$gender + ant$v2)) #ns
summary(lm(ant$Lput_gain-ant$Lput_nongain ~ (ant$ELS.subj * ant$gender) + ant$v2)) #ns
summary(lm(ant$Lput_gain-ant$Lput_nongain ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2))
summary(lm(ant$Lput_gain-ant$Lput_nongain ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

#ant loss v nonloss
summary(lm(ant$Lput_loss-ant$Lput_nonloss ~ ant$ELS.subj + ant$v2)) 
summary(lm(ant$Lput_loss-ant$Lput_nonloss ~ ant$ELS.subj + ant$gender + ant$v2))
summary(lm(ant$Lput_loss-ant$Lput_nonloss ~ (ant$ELS.subj * ant$gender) + ant$v2))
summary(lm(ant$Lput_loss-ant$Lput_nonloss ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) 
summary(lm(ant$Lput_loss-ant$Lput_nonloss ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

ELScond = c(rep(x=ant$ELS.subjcat3, times = 4)) #rep d$ELS.subjcat2 vector 4 times
Lput.pe = c(ant$Lput_gain,ant$Lput_nongain,ant$Lput_loss,ant$Lput_nonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
Lputbar.els = data.frame(condition.2,Lput.pe,ELScond) #concatenate vectors
Lput.means = aggregate(Lputbar.els$Lput.pe, list(ELS = Lputbar.els$ELScond, cond = Lputbar.els$condition.2), mean) #sort pe means by condition and ELS cat
Lput.sd = aggregate(Lputbar.els$Lput.pe, list(ELS = Lputbar.els$ELScond, cond = Lputbar.els$condition.2), sd)
Lput.n = aggregate(Lputbar.els$Lput.pe, list(ELS = Lputbar.els$ELScond, cond = Lputbar.els$condition.2), length)

Lput.summary.els = data.frame(
  Lput.means,  #x = mean
  sd = Lput.sd[3], #x.1 = sd
  n = Lput.n[3]) #x.2 = n

#calculate standard error of the mean 
Lput.summary.els$sem = Lput.summary.els$x.1/sqrt(Lput.summary.els$x.2) 
factor(Lput.summary.els$ELS)
Lput.summary.els$ELS = c(rep(c("low","high"), times = 4))

colors = rep(c("violetred4","red3"),4)

limits = aes(ymin=x-sem, ymax=x+sem)
g6.ELS = ggplot(Lput.summary.els, aes(x = cond, y = x, fill = ELS)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  #ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #theme(legend.key = element_rect(fill = "white")) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_text(size = 20)) + 
  theme(axis.text = element_text(size = 20)) +
  scale_fill_manual(values=colors)
print(g6.ELS)
```

Left Insula
---------------
```{r}
summary(lm(ant$Lins_gain-ant$Lins_nongain ~ ant$ELS.subj + ant$v2)) #ns
summary(lm(ant$Lins_gain-ant$Lins_nongain ~ ant$ELS.subj + ant$gender + ant$v2)) #ns
summary(lm(ant$Lins_gain-ant$Lins_nongain ~ (ant$ELS.subj * ant$gender) + ant$v2)) #ns
summary(lm(ant$Lins_gain-ant$Lins_nongain ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2))
summary(lm(ant$Lins_gain-ant$Lins_nongain ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

#ant loss v nonloss
summary(lm(ant$Lins_loss-ant$Lins_nonloss ~ ant$ELS.subj + ant$v2)) 
summary(lm(ant$Lins_loss-ant$Lins_nonloss ~ ant$ELS.subj + ant$gender + ant$v2))
summary(lm(ant$Lins_loss-ant$Lins_nonloss ~ (ant$ELS.subj * ant$gender) + ant$v2))
summary(lm(ant$Lins_loss-ant$Lins_nonloss ~ (ant$ELS.subjcat2 * ant$gender) + ant$v2)) 
summary(lm(ant$Lins_loss-ant$Lins_nonloss ~ (ant$ELS.subjcat3 * ant$gender) + ant$v2))

ELScond = c(rep(x=ant$ELS.subjcat3, times = 4)) #rep d$ELS.subjcat2 vector 4 times
Lins.pe = c(ant$Lins_gain,ant$Lins_nongain,ant$Lins_loss,ant$Lins_nonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
Linsbar.els = data.frame(condition.2,Lins.pe,ELScond) #concatenate vectors
Lins.means = aggregate(Linsbar.els$Lins.pe, list(ELS = Linsbar.els$ELScond, cond = Linsbar.els$condition.2), mean) #sort pe means by condition and ELS cat
Lins.sd = aggregate(Linsbar.els$Lins.pe, list(ELS = Linsbar.els$ELScond, cond = Linsbar.els$condition.2), sd)
Lins.n = aggregate(Linsbar.els$Lins.pe, list(ELS = Linsbar.els$ELScond, cond = Linsbar.els$condition.2), length)

Lins.summary.els = data.frame(
  Lins.means,  #x = mean
  sd = Lins.sd[3], #x.1 = sd
  n = Lins.n[3]) #x.2 = n

#calculate standard error of the mean 
Lins.summary.els$sem = Lins.summary.els$x.1/sqrt(Lins.summary.els$x.2) 
factor(Lins.summary.els$ELS)
Lins.summary.els$ELS = c(rep(c("low","high"), times = 4))

colors = rep(c("violetred4","red3"),4)

limits = aes(ymin=x-sem, ymax=x+sem)
g5.ELS = ggplot(Lins.summary.els, aes(x = cond, y = x, fill = ELS)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  #ggtitle("Anticipatory L Caud Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #theme(legend.key = element_rect(fill = "white")) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_text(size = 20)) + 
  theme(axis.text = element_text(size = 20)) +
  scale_fill_manual(values=colors)
print(g5.ELS)


```

vmPFC cluster from gender
-----------------------------
```{r}
pfc = read.csv("Model5.1_vmpfc26-Mar-2015.csv")
pfc = cbind(pfc,b)
pfc$gender = as.factor(pfc$gender)
pfc$v2 = as.factor(pfc$v2)
levels(pfc$gender) = c("F","M")

hist(pfc$ELS.subj)
pfc$ELS.subjcat2 = cut(pfc$ELS.subj, c(0,5,10,30), right=FALSE, labels=c("low","int","high")) 
pfc$ELS.subjcat3 = cut(pfc$ELS.subj, c(0,5,30), right=FALSE, labels=c("low","high"))

#outcome gain v nongain

summary(lm(pfc$gain-pfc$nongain ~ pfc$ELS.subj + pfc$v2))
summary(lm(pfc$gain-pfc$nongain ~ pfc$ELS.subj + pfc$gender + pfc$v2))
summary(lm(pfc$gain-pfc$nongain ~ (pfc$ELS.subjcat3 * pfc$gender) + pfc$v2))

#outcome gain v loss
summary(lm(pfc$gain-pfc$loss ~ pfc$ELS.subj + pfc$v2))
summary(lm(pfc$gain-pfc$loss ~ pfc$ELS.subj + pfc$gender + pfc$v2))
summary(lm(pfc$gain-pfc$nonloss ~ (pfc$ELS.subjcat3 * pfc$gender) + pfc$v2))

#ant gain
summary(lm(pfc$antgain ~ pfc$gender + pfc$v2))

t.test(pfc$antgain[pfc$gender=="F"],pfc$antgain[pfc$gender=="M"])

#ant gain v loss
summary(lm(pfc$antgain-pfc$antloss ~ pfc$ELS.subj + pfc$v2))
summary(lm(pfc$antgain-pfc$antloss ~ pfc$gender + pfc$v2))
summary(lm(pfc$antgain-pfc$antloss ~ pfc$ELS.subj + pfc$gender + pfc$v2))
summary(lm(pfc$antgain-pfc$antloss ~ (pfc$ELS.subj * pfc$gender) + pfc$v2))
summary(lm(pfc$antgain-pfc$antloss ~ (pfc$ELS.subjcat2 * pfc$gender) + pfc$v2))
summary(lm(pfc$antgain-pfc$antloss ~ (pfc$ELS.subjcat3 * pfc$gender) + pfc$v2))

vmpfc.pe = c(pfc$antgain,pfc$antnongain,pfc$antloss,pfc$antnonloss)
condition.2 = c(rep(x = "gain", times = 70), rep(x = "nongain", times = 70), rep(x = "loss", times = 70), rep(x = "nonloss", times = 70))
vmpfcbar = data.frame(condition.2,vmpfc.pe)

vmpfc.summary = data.frame(
  condition = levels(vmpfcbar$condition.2),
  mean = tapply(vmpfcbar$vmpfc.pe, vmpfcbar$condition, mean),
  n = tapply(vmpfcbar$vmpfc.pe, vmpfcbar$condition, length),
  sd = tapply(vmpfcbar$vmpfc.pe, vmpfcbar$condition, sd)
  )

#calculate standard error of the mean 
vmpfc.summary$sem = vmpfc.summary$sd/sqrt(vmpfc.summary$n) 

#calculate margin of error for CI
alpha = .05 #95% confidence interval
vmpfc.summary$me = qt(1-alpha/2, df = vmpfc.summary$n)*vmpfc.summary$sem

#error bars represent standard error of the mean
g2.SE = ggplot(vmpfc.summary, aes(x = condition, y = mean)) + 
  geom_bar(position = position_dodge(), stat="identity", fill="red", width=.5) +
  geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem), width=.3) +
  labs(x = "Anticipation", y = "Percent BOLD signal change in vmpfc") +
  #scale_y_continuous(limits=c(-.3, .4)) +
  ggtitle("Anticipatory vmpfc Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) 
print(g2.SE)



#gender plot
Gcond = c(rep(x=pfc$gender, times = 2)) #rep d$ELS.subjcat2 vector 4 times
vmpfcbar.G = data.frame(condition.2,vmpfc.pe,Gcond) #concatenate vectors
vmpfc.means = aggregate(vmpfcbar.G$vmpfc.pe, list(G = vmpfcbar.G$Gcond, cond = vmpfcbar.G$condition.2), mean) #sort pe means by condition and ELS cat
vmpfc.sd = aggregate(vmpfcbar.G$vmpfc.pe, list(G = vmpfcbar.G$Gcond, cond = vmpfcbar.G$condition.2), sd)
vmpfc.n = aggregate(vmpfcbar.G$vmpfc.pe, list(G = vmpfcbar.G$Gcond, cond = vmpfcbar.G$condition.2), length)

vmpfc.summary.G = data.frame(
  vmpfc.means,  #x = mean
  sd = vmpfc.sd[3], #x.1 = sd
  n = vmpfc.n[3]) #x.2 = n

#calculate standard error of the mean 
vmpfc.summary.G$sem = vmpfc.summary.G$x.1/sqrt(vmpfc.summary.G$x.2) 
factor(vmpfc.summary.G$G)
vmpfc.summary.G$G = c(rep(c("female","male"), times = 4))

colors = rep(c("indianred1","orange1"),4)

limits = aes(ymin=x-sem, ymax=x+sem)
g6.ELS = ggplot(vmpfc.summary.G, aes(x = cond, y = x, fill = G)) +  
  geom_bar(stat="identity",position=position_dodge(), width = .75) +
  geom_errorbar(limits,position=position_dodge(width=.75), width = .5) +
  theme_bw() +
  theme(panel.grid.major = element_blank()) + 
  theme(axis.title.y = element_blank()) + theme(axis.title.x = element_blank()) + 
  #labs(x = "Anticipation", y = "% BOLD signal change") +
  #scale_y_continuous(limits=c(-.35, .5)) +
  #ggtitle("Anticipatory vmpfc Activity") +
  geom_hline(yintercept=0, linetype = 1) +
  #theme(panel.grid.major = element_blank()) + 
  theme(legend.text = element_text(size = 20)) + 
  theme(legend.title = element_blank()) + 
  theme(axis.text = element_text(size = 20)) +
  scale_fill_manual(values=colors)
  
print(g6.ELS)

qplot(x=pfc$gender, y = pfc$gain-pfc$loss)

#ant gain
summary(lm(pfc$antgain ~ pfc$gender + pfc$v2))
